Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-08-26 Thesis/chapter/03-theoretical-background.tex
DOE edit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Design of Experiment} %DOE
%\epigraph{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}{Grahem C. Goodwin\cite{goodwin1977experiment}}
%
\begin{quote}
	{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}
	- {Grahem C. Goodwin\cite{goodwin1977experiment}}
\end{quote}
%
In two cases a deliberate design of experiment is beneficial.
If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
If the query space is so vast, that randomly querying might lead to information about uninteresting part of the domain.
% 
At the beginning of an experiment its constraints must be determined. 
%
Constraints for a given experiment might include range of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
%

A naive approach to an experiment design is the full factorial \gls{doe}.
Each possible combination of discrete values is tested. 
While this is the best design it will more often than not be infeasible due the curse of dimensionality.
The 2-level factorial design provides an alternative with $2^d$ (where d is the dimensionality of the problem) experiments. 
Drawbacks of 2-level factorial include no data about the inside of the search space and infeasibility for moderate dimensional problems.

The Plackett-Burman\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of the two level fractional factorial design, 
where the number of needed experiments is smaller than $d+2$ and 
each combination of levels for any pair of factors appears the same number of times. 
In order to overcome these obstacles a certain number of experiments can be chosen randomly from the search space. 
%A straight forward design can be to randomly chose a certain number of experiments from the search space. 
A drawback of randomization is that sample set is likely not evenly distributed across the search space\cite{viana2016tutorial}. 
The Hammersley design\cite{viana2016tutorial,diwekar1997efficient} is based on the Hammersley sequence and produces space filling data points. 
The Latin hypercube \gls{doe}\cite{viana2016tutorial,diwekar1997efficient} is a type of orthogonal \gls{doe}, 
which has the advantage that 
each level for each variable will be tested only once. 
A Latin hypercube \gls{doe} can be also created such that data points more uniformly distribute over the search space. 
%"Our ability to design a good experiment should depend upon our prior knowledge regarding the nature of the data generating mechanism."\cite{goodwin1977experiment}
%
%Continuous state spaces must be accommodated by arbitrary discretization.
\cite{cohn1996neural}
%
At

@@

am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
ist das modell fraglich, sollte man die Daten so erheben, als gälte das nächst kompliziertere Modell \cite{haertler2014statistisch}
Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
Eine gefährliche Fehlerquelle ist dei Erwartung eines bestimmten Ergebnisses durch den Experimentator. \cite{haertler2014statistisch}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Design of Experiment} %DOE
%\epigraph{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}{Grahem C. Goodwin\cite{goodwin1977experiment}}
%
\begin{quote}
	{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}
	- {Grahem C. Goodwin\cite{goodwin1977experiment}}
\end{quote}
%
In two cases a deliberate \gls{doe} is beneficial.
If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
If the query space is so vast, that randomly querying might explore domains which might lead to uninteresting or even misleading information.
% 
At the beginning of an experiment its constraints must be determined. 
%
Constraints for a given experiment might include range of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
%

A naive approach to an experiment design is the full factorial \gls{doe}.
Each possible combination of discrete values is tested. 
While this is the most informative design it will more often than not be infeasible due the curse of dimensionality\cite{cherkassky1998learning}.
The 2-level factorial design provides an alternative with $2^d$ (where $d$ is the number of independent variables) experiments. 
Drawbacks of 2-level factorial include no data about the inside of the search space and infeasibility for moderate dimensional problems.
In a full factorial or 2-level factorial design most experiments are redundant and most resources will be spent exploring high-order interaction effects\cite{gunst2009fractional}.
In order to overcome these obstacles a certain number of experiments can be chosen randomly from the search space. 
%A straight forward design can be to randomly chose a certain number of experiments from the search space.

The Plackett-Burman\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of 2-level fractional factorial design, 
where the number of needed experiments is smaller than $d+2$ and 
each combination of levels for any pair of factors appears the same number of times. 
A drawback of randomization and 2-level factorial designs is that the sample set is likely not evenly distributed across the search space\cite{viana2016tutorial}. 
The Hammersley design\cite{viana2016tutorial,diwekar1997efficient} is based on the Hammersley sequence and produces space filling data points. 
The Latin hypercube \gls{doe}\cite{viana2016tutorial,diwekar1997efficient} is a type of orthogonal \gls{doe}, 
which has the advantage that each level for each variable will be tested only once. 
A Latin hypercube \gls{doe} can be also created such that data points more uniformly distribute over the search space. 
%"Our ability to design a good experiment should depend upon our prior knowledge regarding the nature of the data generating mechanism."\cite{goodwin1977experiment}
%
%Continuous state spaces must be accommodated by arbitrary discretization.
\cite{cohn1996neural}
%
\td{For a 2-level factorial applies: "The effect of any factor main effect (A, B, C) or interaction (AB, AC, BC, ABC) is the difference of two averages, the average of the responses correpsonding to +1 levels and the average of the responses corresponding to -1 levels. " - from Gunst2009\cite{gunst2009fractional}}

@@

am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
"ist das modell fraglich, sollte man die Daten so erheben, als gälte das nächst kompliziertere Modell" \cite{haertler2014statistisch}
Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
Eine gefährliche Fehlerquelle ist dei Erwartung eines bestimmten Ergebnisses durch den Experimentator. \cite{haertler2014statistisch}

\td{if i want to learn about support vector machine, read chapter 4,7,8 from "Learning from Data" by Cherkassky\cite{cherkassky1998learning} (TUBib 726-1998)}

### 2022-08-26 Thesis/chapter/06-results-and-discussion.tex
DOE edit

>>>>

\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest. Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e., that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2007 
but on the other hand 
If one ain't sure a if factor is relevant, the model should be able to detect if there is a influence. - from Haertler2014?
